Looking for a Signal in the Noise: Revisiting Obesity and the microbiome

### 2016-03-23 Sze_ObesityMicrobiomeMetaNoMetaHit_PeerJ_2016.Rmd
combined n power sim add

>>>>

Using a small (0.2), medium (0.5), and large (0.8) cohen value we estimated the power of the combined data set as well as the average cohen value from across studies for Shannon Diversity (0.06) and BF ratio (0.01).

small effect for combined data power calculation:
`r format(round(pwr.t2n.test(n1=length(which(group.data.test$obese == "No")), n2=length(which(group.data.test$obese == "Yes")), d=0.2, sig.level = 0.05, alternative="two.sided")$power,2), nsmall=2)`  
medium effect for combined data power calculation:
`r format(round(pwr.t2n.test(n1=length(which(group.data.test$obese == "No")), n2=length(which(group.data.test$obese == "Yes")), d=0.5, sig.level = 0.05, alternative="two.sided")$power,2), nsmall=2)`  
large effect for combined data power calculation:
`r format(round(pwr.t2n.test(n1=length(which(group.data.test$obese == "No")), n2=length(which(group.data.test$obese == "Yes")), d=0.8, sig.level = 0.05, alternative="two.sided")$power,2), nsmall=2)`  
average effect for all Shannon Diversity:
`r format(round(pwr.t2n.test(n1=length(which(group.data.test$obese == "No")), n2=length(which(group.data.test$obese == "Yes")), d=0.06, sig.level = 0.05, alternative="two.sided")$power,2), nsmall=2)`  
average effect for all BF ratio:
`r format(round(pwr.t2n.test(n1=length(which(group.data.test$obese == "No")), n2=length(which(group.data.test$obese == "Yes")), d=0.01, sig.level = 0.05, alternative="two.sided")$power,2), nsmall=2)`
